%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV for J. Hoar
% makes use of public LaTeX template available at https://www.latextemplates.com/template/developer-cv
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\makeatletter
\let\conditionalinput\@input
\makeatother

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligned minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, ringuce the font size or make the minipage wider and ringuce the others proportionately
	\colorbox{gray}{{\HUGE\textcolor{white}{\textbf{Joanne}}}} % First name
           \\
	\colorbox{gray}{{\HUGE\textcolor{white}{\textbf{Hoar}}}} % Last name
	
	
	\vspace{6pt}
	
	{\huge Senior Software Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligned minipages

	\conditionalinput{privatecontact.tex} %optional
	\textvisiblespace  %column appears if empty
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligned minipages	

% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (suppliing with the template) and using the word after \fa in the command for the icon you want
	\icon{Discord}{12}{\href{https://discordapp.com/users/jo.codegirl}{discord: jo.codegirl}}\\
	\icon{Globe}{12}{\href{https://linkedin.com/in/joanne-hoar/}{linkedin: joanne-hoar}}\\
	\icon{Github}{12}{\href{https://github.com/xcodegirl}{github: xcodegirl}}\\
\end{minipage}
 
\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	Canadian Software Developer with 20 years of experience in video game programming, scientific modelling and cross-platform development. Expertise in multiple programming languages, game engines and SDKs. Proven track record in leading teams, mentoring developers, impressing customers and building corporate culture. Strong background in C++, Unreal Engine, iOS and Android using agile methodologies and CI/CD. Passion for algorithmic correctness, mathematics, artificial intelligence and nature.
\end{minipage}

\conditionalinput{specialpurpose.tex} % optional intro section

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
 
\cvsect{Experience}

\begin{entrylist}
	\entry
		{Jan 2025 -- present}
		{Technology Instructor}
		{Robertson College (contract)}
		{Develop and deliver interactive course materials for 50+ students per term, Manage and update a GitHub repository hosting open-source course materials, Host live coding sessions, debugging student projects in real-time and archiving recordings for asynchronous review, Participate in ongoing professional development, including monthly instructor training seminars.\\ 
\texttt{C\#}\slashsep\texttt{Databases}\slashsep\texttt{ASP .Net Core}\slashsep\texttt{Front End Frameworks}\slashsep\texttt{Javascript}\slashsep\texttt{Java}\slashsep\texttt{GitHub}\slashsep\texttt{Azure}}
	\entry
		{2022 -- 2025}
		{Senior Software Developer}
		{bitHeads Inc.}
		{Developed and maintained cross-platform client API for BaaS to add gamification and real-time multiplayer tech for AAA and Indie Studios. Developed and released demo games and projects. Engineered and maintained CI/CD and TDD pipeline. Responded to customer issues and feature requests.\\ \texttt{Unreal Engine}\slashsep\texttt{C++}\slashsep\texttt{Objective-C, Swift}\slashsep\texttt{iOS}\slashsep\texttt{Android Native}\slashsep\texttt{Java}\slashsep\texttt{PlayStation}\slashsep\texttt{Node.js}\slashsep\texttt{Groovy}\slashsep\texttt{C\# (Unity, Godot)}\slashsep\texttt{Shell Script}\slashsep\texttt{MacOS}\slashsep\texttt{Windows}\slashsep\texttt{Linux}}
\entry
		{2011 -- 2022}
		{Co-founder/ Lead Developer}
		{Silicon Hanna Inc. (self-employed)}
		{Designed, coded and published nine games to commercial app stores for mobile devices. Experimented with cutted edge device tech and SDKs.\\ \texttt{Unreal Engine}\slashsep\texttt{Objective-C / Swift}\slashsep\texttt{iOS}\slashsep\texttt{Android Native}\slashsep\texttt{Kotlin}\slashsep\texttt{Augmented Reality}\slashsep\texttt{MacOS}\slashsep\texttt{Windows}}
	\entry
		{2008 -- 2011}
		{Tools Programmer}
		{Fekete Associates Inc. (S\&P Global)}
		{Developed tools used mathematical modelled to maximize production and improve efficiency for major oil \& gas corporations. Led research on a new system that reduced build times by 40\%. \\ \texttt{C++}\slashsep\texttt{MFC}\slashsep\texttt{Windows}}
	\entry
		{2005 -- 2008}
		{Intermediate Software Engineer}
		{BJ Pipeline Inspection Services Inc. (Baker Hughes)}
		{Visualised in-line device data with OpenGL graphics. Implemented neural network algorithms for anomaly detection. Led development of custom web-based GIS reported software. Improved low-level programming algorithms for data processing.\\ \texttt{C++}\slashsep\texttt{C}\slashsep\texttt{OpenGL}\slashsep\texttt{PHP}\slashsep\texttt{SQL}\slashsep\texttt{Neural Networks}\slashsep\texttt{Borland}\slashsep\texttt{Windows}\slashsep\texttt{Linux}}
	\entry
		{2005 -- 2008}
		{Co-founder / App Developer / Instructor}
		{SuRJE Software Solutions Inc. (self-employed, contract)}
		{Created and published physics-based games for iOS. Technical writing, web development, google maps and firebase integration and server administration. Developed course curriculum, instructed C++ programming and assessed student work with Department of Continued Education.\\ \texttt{C++}\slashsep\texttt{C}\slashsep\texttt{OpenGL}\slashsep\texttt{PHP}\slashsep\texttt{SQL}\slashsep\texttt{Neural Networks}\slashsep\texttt{Borland}\slashsep\texttt{Windows}\slashsep\texttt{Linux}}
	\entry
		{2005 - 2006}
		{Software Researcher / Lead Developer}
		{PlayStarMusic Corp.}
		{Lead developer and system administrator for an iTunes like music store. Automated DRM encoded and video streamed. Developed a prototype for a Google competitive search engine.
\\ \texttt{C++}\slashsep\texttt{PHP}\slashsep\texttt{Javascript}\slashsep\texttt{.NET}\slashsep\texttt{Windows}\slashsep\texttt{Linux}}
	\entry
		{2004 - 2005}
		{Junior Software Engineer}
		{Codefast.com }
		{Ported applications to operate under a new GUI library. Developed user interfaces for software lifecycle automation.\\ \texttt{C++}\slashsep\texttt{Shell script}\slashsep\texttt{Windows}\slashsep\texttt{Unix}\slashsep\texttt{Qt}\slashsep\texttt{Wx}}
	\entry
		{2001 - 2004}
		{Research Assistant}
		{VLab Computer Graphics Group / Artificial Intelligence Research Hub}
		{Developed graphics software tools used fractal math and biological modelling. Managed network setup and code base for distributed computing. Participated in interdepartmental projetcs, published five research papers, led student tutorials and marked assignments.\\ \texttt{C++}\slashsep\texttt{OpenGL}\slashsep\texttt{Solaris}\slashsep\texttt{MacOS}\slashsep\texttt{Unix}\slashsep\texttt{Linux}\slashsep\texttt{PHP}\slashsep\texttt{MySQL}\slashsep\texttt{Qt}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{education}

\begin{entrylist}
	\entry
		{2002 -- 2004}
		{Master's Degree}
		{University of Calgary}
		{Computer Science\\\footnotesize{{\sl Thesis Title:} Agent-based Development of Natural Transportation Networks}}
	\entry
		{1998 -- 2001}
		{Bachelor's Degree}
		{University of Calgary}
		{Computer Science}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------
\cvsect{Community Outreach}

$\bullet$ Treasurer, Hanna \& District Minor Soccer Association, 2025 - present
\\$\bullet$ Vice President, Hanna Figure Skating Club, 2024 - present
\\ $\bullet$ Costume Coordinator, Stage Hanna Junior, 2024
\\ $\bullet$ Women of bitHeads and Cookbook Committee, bitHeads, 2024 
\\ $\bullet$ Team Manager/Assistant Coach, U11 Soccer, 2024
\\ $\bullet$ Dryland Training Coordinator, Hanna Figure Skating Club, 2022 - 2024
\\ $\bullet$ 4-H Public Speaking Judge, District Level Competition, 2022
\\ $\bullet$ Computer Programming for Kids, J.C. Charyk School, 2019 - 2021
\\ $\bullet$ Reading Program, Our Lady of Fatima School, 2016 - 2018
\\ $\bullet$ Preschool Gym Leader, YMCA,  2013 - 2014
\\ $\bullet$ OpenGL Elective Instructor, Fekete Associates, 2010
\\ $\bullet$ Calgary Corporate Challenge, 2007 - 2008
\\ $\bullet$ Ladies Golf and Luncheon Club Coordinator, BJ Pipeline Inspection, 2006 - 2008 
\\ $\bullet$ SCIberMENTOR, 2002 - 2005
\\ $\bullet$ President, Computer Science Graduate Society, 2002 - 2003
\\ $\bullet$ VP Academic, Computer Science Undergraduate Society, 2001 - 2001

	\cvsect{Awards}

$\bullet$ Departmental Nomination: Governor General's Gold Medal, Faculty of Graduate Studies, 2005
\\ $\bullet$ Postgraduate Scholarship NSERC D3, Natural Sciences and Engineering Research Council of Canada, 2005
\\ $\bullet$ Graduate Student Scholarship, Alberta Learning, 2004
\\ $\bullet$ Best Student Paper Award (Co-author), ACAL 2003
\\ $\bullet$ CPSC Departmental Research Award, University of Calgary, 2003

\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligned minipages

	\cvsect{Languages}
	
	\textbf{English} - native\\
	\textbf{French} - intermediate\\
	\textbf{Spanish} - rudimentary

\cvsect{Work Samples}

\icon{Github}{12} {\href{https://github.com/xcodegirl/career/blob/main/xcodegirl-work-samples.md}{github.com: xcodegirl/career}}.

\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligned minipages
	
	\cvsect{Published Games}

$\bullet$ Ragin’ Bull - iOS, Android (2020)
\\ $\bullet$ AR Picture Portal - iOS (2018)
\\ $\bullet$ Fragment Reality - iOS (2018)
\\ $\bullet$ IceCream AR - iOS (2018)
\\ $\bullet$ Jewel Slide - iOS (2017), Android (2019)
\\ $\bullet$ Word Slide \& Find - iOS (2017)
\\ $\bullet$ A Word Theme - iOS (2017), Android (2019)
\\ $\bullet$ CryptoQuip - iOS (2011), Android (2019)
\\ $\bullet$ Rafter’s Loot - iOS (2011)
\\ $\bullet$ Star Chase - iOS (2008)
\\ $\bullet$ Bitsy - iOS (2008)

\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
