\cvsect{Teaching Ideology}

\begin{minipage}[t]{\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Requiring for vertically aligning minipages
I strongly believe in experiential learning; students learn best by doing. In a lecture I first share
knowledge on the subject in an inclusive way where students participate and are engaged in the
subject matter. I present material in a clear and organized format with enough flexibility to
accommodate individual student needs and current trends in education and industry. Then it is
important the students have a chance to explore the subject in further detail while I am available
to motivate and clarify. In this way a new subject is introduced then immediately reinforced
through independent learning. This endows students with increased retention of the specific
material in addition to the capacity and confidence to continue learning through life, helping
them excel in future classes and in industry after graduation.

\end{minipage}

\cvsect{Teaching Experience}

\begin{minipage}[t]{\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Requiring for vertically aligning minipages
\begin{entrylist}
	\entry
{}
{}
{}
{At my most recent position as senior software developer I was hired in part based on my educational experience. They needed someone who could teach clients one-on-one how to use the API, someone who had strong documentation skills and could develop academic examples and demonstrations. }
\end{entrylist}
\begin{entrylist}
	\entry
{}
{}
{}
{During my position as software developer at an oil and gas services company I
offered a voluntary course to co-workers on the subject of computer graphics programming
using OpenGL. I successfully designed the course including presentations, sample code and
weekly assignments to accommodate both beginner programmers and senior developers. My
course as presented received a positive response from my students and their senior staff.}
\end{entrylist}
\begin{entrylist}
	\entry
{}
{}
{}
{Prior to this, I taught sessions for Continuing Education at the University of Calgary. The 3 hour
sessions in intermediate programming gave me an opportunity to present the material and
follow up with example code and assignments. The students appreciated my well thought out
lectures and accessible notes, as well as my on-the-spot know-how of the material to help as
they worked through their projects.}
\end{entrylist}
\begin{entrylist}
	\entry
{}
{}
{}
{During my postgraduate studies I particularly enjoyed working as a teaching assistant. Not only
did I offer lab support to students, I complimented the instructors’ lesson plans with my own
presentations of the material, showing more code and math walk-throughs. I found this work to
help me reinforce my own knowledge of the subject in turn improving my own education. This
experience instilled in me an appreciation and love for teaching. I excelled with both introductory
first year and advanced third year material.}
\end{entrylist}
\end{minipage}