\documentclass[10pt]{article}
\usepackage[letterpaper,margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{ragged2e}
\usepackage{moresize}
\usepackage{fontawesome5}
\usepackage[default]{raleway}
\usepackage{multicol}

% Colour scheme
\definecolor{accent}{RGB}{10,60,90}
\definecolor{secondary}{RGB}{30,30,30}

% Font and layout
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\newcommand{\mytitle}[1]{\color{accent}\normalfont\large\bfseries{#1}}
\newcommand{\tech}[1]{\textcolor{secondary}{\textbf{#1}}}

% Section style
\titleformat{\section}{\mytitle}{}{0em}{}[{\titlerule[0.8pt]}]
\titlespacing{\section}{0pt}{9pt}{5pt}

% Bullet list formatting
\setlist[itemize]{leftmargin=*,nosep,after=\vspace{3pt}}
\setlist[itemize]{label=\color{accent}\scriptsize\raisebox{0.4ex}{\textbullet}}

% Custom macros
\newcommand{\experience}[4]{%
  \vspace{4pt}
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & \textit{#2} \\
    \textit{\small#3} & \textit{\small#4}
  \end{tabular*}
  \vspace{-4pt}
}

\begin{document}

% ===== Header =====
\begin{center}
\colorbox{gray}{\HUGE\textcolor{white}{\textbf{Joanne}}} \\[2pt]
\colorbox{gray}{\HUGE\textcolor{white}{\textbf{Hoar}}} \\[6pt]
    {\Large \tech{Technology Educator, Software Developer, Game Developer}} \\[6pt]
    \faIcon{linkedin}~\href{https://linkedin.com/in/joanne-hoar/}{linkedin.com/in/joanne-hoar}\hfill \faIcon{github}~\href{https://github.com/xcodegirl}{xcodegirl}
\end{center}

% ===== Summary =====
\section*{Summary}

Canadian Software Developer with 20 years of experience in video game programming, scientific modelling and cross-platform development. Expertise in multiple programming languages, game engines and SDKs. Proven track record in leading teams, mentoring developers, impressing customers and building corporate culture. Strong background in C++, Unreal Engine, iOS and Android using agile methodologies and CI/CD. Passion for algorithmic correctness, mathematics, artificial intelligence and nature.

% ===== Experience =====
\section*{Experience}

\experience{Technology Instructor}{Jan 2025 -- present}{Robertson College (contract)}{}
\hspace{0.5cm}\texttt{C\# / .NET / ASP .NET Core / Java / JavaScript / React / Git / GitHub / Azure / SQL}
['Instructed 20+ course offerings across Full Stack Development and Data Analytics diploma programs. Delivered live coding sessions, maintained open-source course materials on GitHub, and achieved an average student satisfaction rating of 4.5/5.0.']

\experience{Senior Software Developer}{2022 -- 2025}{bitHeads Inc.}{}
\hspace{0.5cm}\texttt{Unreal Engine / C++ / Objective-C / Swift / iOS / Android Native / Java / Kotlin / PlayStation / Xbox / Nintendo Switch / Node.js / Groovy / C\# / Shell Script}
['Developed and maintained cross-platform client SDKs for a backend-as-a-service platform used by 50+ published games across 12 platforms including PlayStation, Xbox, Nintendo Switch, iOS, and Android. Engineered CI/CD and TDD pipelines and managed customer relationships with AAA and Indie studios.']

\experience{Co-founder/ Lead Developer}{2011 -- 2022}{Silicon Hanna Inc. (self-employed)}{}
\hspace{0.5cm}\texttt{Unreal Engine / Objective-C / Swift / iOS / Android Native / Kotlin / Augmented Reality / MacOS / Windows}
['Designed, coded and published eleven mobile games for iOS and Android, from concept and game design through to commercial app-store release. Experimented with cutting-edge device technologies including ARKit and other emerging SDKs.']

\experience{Tools Programmer}{2008 -- 2011}{Fekete Associates Inc. (S\&P Global)}{}
\hspace{0.5cm}\texttt{C++ / MFC / Windows / Perforce / Incredibuild}
['Developed tools that used mathematical modelling to maximize production and improve efficiency for major oil \& gas corporations. Led research on a new system that reduced build times by 40\%.']

\experience{Intermediate Software Engineer}{2005 -- 2008}{BJ Pipeline Inspection Services Inc. (Baker Hughes)}{}
\hspace{0.5cm}\texttt{C++ / C / OpenGL / PHP / SQL / Neural Networks / Borland / Windows / Linux}
['Visualised in-line device data with OpenGL graphics. Implemented neural network algorithms for anomaly detection. Led development of custom web-based GIS reporting software. Improved low-level programming algorithms for data processing.']

\experience{Co-founder / App Developer / Instructor}{2005 -- 2008}{SuRJE Software Solutions Inc. (self-employed, contract)}{}
\hspace{0.5cm}\texttt{Objective-C / C++ / OpenGL / Chipmunk / PHP / JavaScript / Firebase / Google Maps / iOS / Linux}
['Created and published physics-based games for iOS. Handled technical writing, web development, Google Maps and Firebase integration and server administration. Developed course curriculum, instructed C++ programming and assessed student work with the Department of Continuing Education.']

\experience{Software Researcher / Lead Developer}{2005 - 2006}{PlayStarMusic Corp.}{}
\hspace{0.5cm}\texttt{C++ / PHP / Javascript / .NET / Windows / Linux}
['Led development and system administration for an iTunes-like music store. Automated DRM encoding and video streaming. Developed a prototype for a Google-competitive search engine.']

\experience{Junior Software Engineer}{2004 - 2005}{Codefast.com}{}
\hspace{0.5cm}\texttt{C++ / Qt / Wx / Shell script / Windows / Unix}
['Ported applications to operate under a new GUI library. Developed user interfaces for software lifecycle automation.']

\experience{Web Developer / VR Artist}{2002 -- 2004}{Nickle Arts Museum, University of Calgary (contract)}{}
\hspace{0.5cm}\texttt{JavaScript / C++ / OpenGL / PHP / HTML / CSS / 3D Scanning / VR}
['Designed and developed an interactive online catalogue for the Gerald Hushlak art exhibit with JavaScript-based features. Contributed original generative art from graduate research. Collaborated on a pioneering VR installation using 3D scanning and CAVE immersion technology.']

\experience{Research Assistant}{2001 - 2004}{VLab Computer Graphics Group / Artificial Intelligence Research Hub}{}
\hspace{0.5cm}\texttt{C++ / OpenGL / PHP / MySQL / Qt / Solaris / Unix / Linux}
['Developed graphics software tools using fractal mathematics and biological modelling. Managed network setup and distributed computing infrastructure. Published five research papers and served as teaching assistant across three courses.']

% ===== Education =====
\section*{Education}
\begin{itemize}
    \item \tech{Master's Degree} -- University of Calgary \hfill 2002 -- 2004
    \textit{\small Computer Science}
    \textit{\small Thesis: Agent-based Development of Natural Transportation Networks}
    \item \tech{Bachelor's Degree} -- University of Calgary \hfill 1998 -- 2001
    \textit{\small Computer Science}
\end{itemize}

% ===== Honours & Awards =====
\section*{Honours \& Awards}
\begin{itemize}[nosep,leftmargin=*]
    \item Departmental Nomination: Governor General's Gold Medal -- Faculty of Graduate Studies \hfill 2005
    \item Postgraduate Scholarship NSERC D3 -- Natural Sciences and Engineering Research Council of Canada \hfill 2005
    \item Graduate Student Scholarship -- Alberta Learning \hfill 2004
    \item Best Student Paper Award (Co-author) -- ACAL \hfill 2003
    \item CPSC Departmental Research Award -- University of Calgary \hfill 2003
\end{itemize}

% ===== Portfolio =====
\section*{Portfolio}
\faIcon{github}~\href{https://github.com/xcodegirl/career/blob/main/xcodegirl-work-samples.md}{xcodegirl/career}\\

% ===== Published Games =====
\section*{Published Games}
Ragin' Bull -- iOS, Android (2020)\\
AR Picture Portal -- iOS (2018)\\
Fragmented Reality -- iOS (2018)\\
IceCream AR -- iOS (2018)\\
Jewel Slide -- iOS, Android (2017, 2019)\\
Word Slide \& Find -- iOS (2017)\\
A Word Theme -- iOS, Android (2017, 2019)\\
CryptoQuip -- iOS, Android (2011, 2019)\\
Rafter’s Loot -- iOS (2011)\\
Star Chase -- iOS (2008)\\
Bitsy -- iOS (2008)\\

\end{document}