%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV for Joanne Hoar
% makes use of public LaTeX template available at https://www.latextemplates.com/template/developer-cv
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%      PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv}

%----------------------------------------------------------------------------------------
\begin{document}

%----------------------------------------------------------------------------------------
% TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth}
\colorbox{gray}{\HUGE\textcolor{white}{\textbf{Joanne}}} \\
\colorbox{gray}{\HUGE\textcolor{white}{\textbf{Hoar}}}

{\huge Technology Educator, Software Developer, Game Developer}
\end{minipage}
\begin{minipage}[t]{0.275\textwidth}
\end{minipage}
\begin{minipage}[t]{0.275\textwidth}
\icon{Globe}{12}{\href{https://linkedin.com/in/joanne-hoar/}{linkedin: Joanne Hoar}}\\
\icon{Github}{12}{\href{https://github.com/xcodegirl}{github: xcodegirl}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
% INTRODUCTION
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}
Canadian Software Developer with 20 years of experience in video game programming, scientific modelling and cross-platform development. Expertise in multiple programming languages, game engines and SDKs. Proven track record in leading teams, mentoring developers, impressing customers and building corporate culture. Strong background in C++, Unreal Engine, iOS and Android using agile methodologies and CI/CD. Passion for algorithmic correctness, mathematics, artificial intelligence and nature.

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}
\begin{entrylist}
	\entry
		{Jan 2025 -- present}
		{Technology Instructor}
		{Robertson College (contract)}
		{Instructed 20+ course offerings across Full Stack Development and Data Analytics diploma programs. Delivered live coding sessions, maintained open-source course materials on GitHub, and achieved an average student satisfaction rating of 4.5/5.0.\\ \texttt{C\#}\slashsep\texttt{.NET}\slashsep\texttt{ASP .NET Core}\slashsep\texttt{Java}\slashsep\texttt{JavaScript}\slashsep\texttt{React}\slashsep\texttt{Git}\slashsep\texttt{GitHub}\slashsep\texttt{Azure}\slashsep\texttt{SQL}}
	\entry
		{2022 -- 2025}
		{Senior Software Developer}
		{bitHeads Inc.}
		{Developed and maintained cross-platform client SDKs for a backend-as-a-service platform used by 50+ published games across 12 platforms including PlayStation, Xbox, Nintendo Switch, iOS, and Android. Engineered CI/CD and TDD pipelines and managed customer relationships with AAA and Indie studios.\\ \texttt{Unreal Engine}\slashsep\texttt{C++}\slashsep\texttt{Objective-C}\slashsep\texttt{Swift}\slashsep\texttt{iOS}\slashsep\texttt{Android Native}\slashsep\texttt{Java}\slashsep\texttt{Kotlin}\slashsep\texttt{PlayStation}\slashsep\texttt{Xbox}\slashsep\texttt{Nintendo Switch}\slashsep\texttt{Node.js}\slashsep\texttt{Groovy}\slashsep\texttt{C\#}\slashsep\texttt{Shell Script}}
	\entry
		{2011 -- 2022}
		{Co-founder/ Lead Developer}
		{Silicon Hanna Inc. (self-employed)}
		{Designed, coded and published eleven mobile games for iOS and Android, from concept and game design through to commercial app-store release. Experimented with cutting-edge device technologies including ARKit and other emerging SDKs.\\ \texttt{Unreal Engine}\slashsep\texttt{Objective-C / Swift}\slashsep\texttt{iOS}\slashsep\texttt{Android Native}\slashsep\texttt{Kotlin}\slashsep\texttt{Augmented Reality}\slashsep\texttt{MacOS}\slashsep\texttt{Windows}}
	\entry
		{2008 -- 2011}
		{Tools Programmer}
		{Fekete Associates Inc. (S\&P Global)}
		{Developed tools that used mathematical modelling to maximize production and improve efficiency for major oil \& gas corporations. Led research on a new system that reduced build times by 40\%.\\ \texttt{C++}\slashsep\texttt{MFC}\slashsep\texttt{Windows}}
	\entry
		{2005 -- 2008}
		{Intermediate Software Engineer}
		{BJ Pipeline Inspection Services Inc. (Baker Hughes)}
		{Visualised in-line device data with OpenGL graphics. Implemented neural network algorithms for anomaly detection. Led development of custom web-based GIS reporting software. Improved low-level programming algorithms for data processing.\\ \texttt{C++}\slashsep\texttt{C}\slashsep\texttt{OpenGL}\slashsep\texttt{PHP}\slashsep\texttt{SQL}\slashsep\texttt{Neural Networks}\slashsep\texttt{Borland}\slashsep\texttt{Windows}\slashsep\texttt{Linux}}
	\entry
		{2005 -- 2008}
		{Co-founder / App Developer / Instructor}
		{SuRJE Software Solutions Inc. (self-employed, contract)}
		{Created and published physics-based games for iOS. Technical writing, web development, Google Maps and Firebase integration and server administration. Developed course curriculum, instructed C++ programming and assessed student work with the Department of Continuing Education.\\ \texttt{Objective-C}\slashsep\texttt{C++}\slashsep\texttt{OpenGL}\slashsep\texttt{Chipmunk}\slashsep\texttt{PHP}\slashsep\texttt{JavaScript}\slashsep\texttt{Firebase}\slashsep\texttt{Google Maps}\slashsep\texttt{iOS}\slashsep\texttt{Linux}}
	\entry
		{2005 - 2006}
		{Software Researcher / Lead Developer}
		{PlayStarMusic Corp.}
		{Lead developer and system administrator for an iTunes-like music store. Automated DRM encoding and video streaming. Developed a prototype for a Google-competitive search engine.\\ \texttt{C++}\slashsep\texttt{PHP}\slashsep\texttt{Javascript}\slashsep\texttt{.NET}\slashsep\texttt{Windows}\slashsep\texttt{Linux}}
	\entry
		{2004 - 2005}
		{Junior Software Engineer}
		{Codefast.com}
		{Ported applications to operate under a new GUI library. Developed user interfaces for software lifecycle automation.\\ \texttt{C++}\slashsep\texttt{Qt}\slashsep\texttt{Wx}\slashsep\texttt{Shell script}\slashsep\texttt{Windows}\slashsep\texttt{Unix}}
	\entry
		{2002 -- 2004}
		{Web Developer / VR Artist}
		{Nickle Arts Museum, University of Calgary (contract)}
		{Designed and developed an interactive online catalogue for the Gerald Hushlak art exhibit with JavaScript-based features. Contributed original generative art from graduate research. Collaborated on a pioneering VR installation using 3D scanning and CAVE immersion technology.\\ \texttt{JavaScript}\slashsep\texttt{C++}\slashsep\texttt{OpenGL}\slashsep\texttt{PHP}\slashsep\texttt{HTML}\slashsep\texttt{CSS}\slashsep\texttt{3D Scanning}\slashsep\texttt{VR}}
	\entry
		{2001 - 2004}
		{Research Assistant}
		{VLab Computer Graphics Group / Artificial Intelligence Research Hub}
		{Developed graphics software tools using fractal mathematics and biological modelling. Managed network setup and distributed computing infrastructure. Published five research papers and served as teaching assistant across three courses.\\ \texttt{C++}\slashsep\texttt{OpenGL}\slashsep\texttt{PHP}\slashsep\texttt{MySQL}\slashsep\texttt{Qt}\slashsep\texttt{Solaris}\slashsep\texttt{Unix}\slashsep\texttt{Linux}}
\end{entrylist}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{education}
\begin{entrylist}
	\entry
		{2002 -- 2004}
		{Master's Degree}
		{University of Calgary}
		{Computer Science\\\footnotesize{{\sl Thesis Title:} Agent-based Development of Natural Transportation Networks}}
	\entry
		{1998 -- 2001}
		{Bachelor's Degree}
		{University of Calgary}
		{Computer Science}
\end{entrylist}

%----------------------------------------------------------------------------------------
% AWARDS
%----------------------------------------------------------------------------------------

\cvsect{Awards}
$\bullet$ Departmental Nomination: Governor General's Gold Medal, Faculty of Graduate Studies, 2005\\
$\bullet$ Postgraduate Scholarship NSERC D3, Natural Sciences and Engineering Research Council of Canada, 2005\\
$\bullet$ Graduate Student Scholarship, Alberta Learning, 2004\\
$\bullet$ Best Student Paper Award (Co-author), ACAL, 2003\\
$\bullet$ CPSC Departmental Research Award, University of Calgary, 2003\\

%----------------------------------------------------------------------------------------
% ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth}
\cvsect{Languages}
\textbf{English} - native\\
\textbf{French} - intermediate\\
\textbf{Spanish} - rudimentary\\
\cvsect{Portfolio}
\icon{Github}{12}{\href{https://github.com/xcodegirl/career}{github.com: xcodegirl/career}}.
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
\cvsect{Published Games}
$\bullet$ Ragin' Bull - iOS, Android (2020)\\
$\bullet$ AR Picture Portal - iOS (2018)\\
$\bullet$ Fragmented Reality - iOS (2018)\\
$\bullet$ IceCream AR - iOS (2018)\\
$\bullet$ Jewel Slide - iOS, Android (2017, 2019)\\
$\bullet$ Word Slide \& Find - iOS (2017)\\
$\bullet$ A Word Theme - iOS, Android (2017, 2019)\\
$\bullet$ CryptoQuip - iOS, Android (2011, 2019)\\
$\bullet$ Rafter's Loot - iOS (2011)\\
$\bullet$ Star Chase - iOS (2008)\\
$\bullet$ Bitsy - iOS (2008)\\
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}