\documentclass[10pt]{article}
\usepackage[letterpaper,margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{ragged2e}
\usepackage{moresize}
\usepackage{fontawesome5}
\usepackage[default]{raleway}
\usepackage{multicol}

% Colour scheme
\definecolor{accent}{RGB}{10,60,90}
\definecolor{secondary}{RGB}{30,30,30}

% Font and layout
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\newcommand{\mytitle}[1]{\color{accent}\normalfont\large\bfseries{#1}}
\newcommand{\tech}[1]{\textcolor{secondary}{\textbf{#1}}}

% Section style
\titleformat{\section}{\mytitle}{}{0em}{}[{\titlerule[0.8pt]}]
\titlespacing{\section}{0pt}{9pt}{5pt}

% Bullet list formatting
\setlist[itemize]{leftmargin=*,nosep,after=\vspace{3pt}}
\setlist[itemize]{label=\color{accent}\scriptsize\raisebox{0.4ex}{\textbullet}}

% Custom macros
\newcommand{\experience}[4]{%
  \vspace{4pt}
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & \textit{#2} \\
    \textit{\small#3} & \textit{\small#4}
  \end{tabular*}
  \vspace{-4pt}
}

\begin{document}

% ===== Header =====
\begin{center}
\colorbox{gray}{\HUGE\textcolor{white}{\textbf{Alex}}} \\[2pt]
\colorbox{gray}{\HUGE\textcolor{white}{\textbf{Example}}} \\[6pt]
    {\Large \tech{Full Stack Developer}} \\[6pt]
    \faIcon{at}~\href{mailto:alex@example.com}{alex@example.com}\hfill \faIcon{phone}~(555) 123-4567\hfill \faIcon{linkedin}~\href{https://www.linkedin.com/company/linkedin/}{linkedin.com/in/linkedin}\hfill \faIcon{github}~\href{https://github.com/github}{github}
\end{center}

% ===== Summary =====
\section*{Summary}

Creative developer with 10 years of experience in web and cloud technologies. Expertise in modern frameworks and cloud infrastructure. Proven ability to lead teams and deliver scalable solutions.

% ===== Experience =====
\section*{Experience}

\experience{Lead Developer}{2022 -- present}{ExampleSoft}{}
\hspace{0.5cm}\texttt{Python / Django / React / AWS / Docker / Kubernetes}
\begin{itemize}
    \item Leading a team of 8 developers to deliver SaaS products for global clients. Architected microservices and CI/CD pipelines. Mentored junior engineers.
\end{itemize}

\experience{Software Engineer}{2017 -- 2022}{Webify Inc.}{}
\hspace{0.5cm}\texttt{Node.js / Express / Vue.js / MongoDB / Jenkins}
\begin{itemize}
    \item Developed REST APIs and modern web applications. Automated testing and deployment pipelines. Improved system performance by 40\%.
\end{itemize}

% ===== Education =====
\section*{Education}
\begin{itemize}
    \item \tech{BSc} -- Wonderland University \hfill 2013 -- 2017
    \textit{\small Computer Science}
\end{itemize}

% ===== Certifications =====
\section*{Certifications}
\begin{itemize}[nosep,leftmargin=*]
    \item AWS Certified Solutions Architect -- Amazon Web Services \hfill 2023
         (ID: AWS-12345678)
    \item Kubernetes Application Developer -- Linux Foundation \hfill 2022
         (ID: LFCD-2022-001)
\end{itemize}

% ===== Honours & Awards =====
\section*{Honours \& Awards}
\begin{itemize}[nosep,leftmargin=*]
    \item Developer of the Year -- Webify Inc. \hfill 2021
    \item Open Source Contributor Award -- Tech Community Alliance \hfill 2023
\end{itemize}

% ===== Technical Skills =====
\section*{Technical Skills}
\textbf{Backend Languages:} Python, JavaScript/Node.js, Go, Java \\
\textbf{Frontend Frameworks:} React, Vue.js, Angular, TypeScript \\
\textbf{Cloud \& DevOps:} AWS, Google Cloud, Docker, Kubernetes, Terraform \\
\textbf{Databases:} PostgreSQL, MongoDB, Redis, DynamoDB \\

% ===== Projects =====
\section*{Projects}
\textbf{Real-time Analytics Dashboard} \hfill 2023 \\
Built a high-performance dashboard processing 1M+ events daily using React and Kafka. \\
\textcolor{secondary}{\textbf{Technologies:}} React, Node.js, Kafka, PostgreSQL \\

\textbf{Microservices Framework} \hfill 2021 -- present \\
Open-source framework for building scalable microservices with built-in observability. \\
\textcolor{secondary}{\textbf{Technologies:}} Go, gRPC, Docker \\

% ===== Volunteer Experience =====
\section*{Volunteer Experience}
\textbf{Technical Mentor} \hfill 2020 -- present \\
\textit{Code for Good} \\
Mentoring junior developers from underrepresented backgrounds. Led workshops on cloud architecture and DevOps practices. \\

% ===== Publications =====
\section*{Publications}
\begin{itemize}[nosep,leftmargin=*]
    \item Scaling Microservices: Best Practices and Pitfalls (Dev.to) \hfill 2023
    \item Kubernetes in Production: Lessons Learned (Medium) \hfill 2022
\end{itemize}

% ===== Languages =====
\section*{Languages}
\begin{itemize}
    \item \textbf{English} -- native
    \item \textbf{Spanish} -- intermediate
    \item \textbf{Mandarin} -- beginner
\end{itemize}

% ===== Professional Memberships =====
\section*{Professional Memberships}
\begin{itemize}[nosep,leftmargin=*]
    \item ACM (Member) \hfill 2018 -- present
    \item Cloud Native Computing Foundation (Member) \hfill 2021 -- present
\end{itemize}

% ===== Portfolio =====
\section*{Portfolio}
\faIcon{github}~\href{https://github.com/github}{GitHub Portfolio}\\
\faIcon{globe}~\href{https://google.com}{Personal Website}\\

\end{document}